DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-08 child_single_geo.Rmd
stores score_breakdowns, fixes loop printing

```{r} 
#library(broom)

this_geo <- st_as_sf(loop_df) %>% filter(tomatch == "{{current_geo}}") 
this_roads <- st_intersection(ncdf, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))

# need to handle the case where this_sw_sh or this_roads has 0 rows
has_roads <- nrow(this_roads) != 0
has_sw_sh <- nrow(this_sw_sh) != 0
has_both <- has_roads & has_sw_sh
# do not evaluate most of this child if does not
```

@@

```{r, eval=has_sw_sh & !has_roads}
this_centerline_miles <- 0 # this_centerline_miles is CENTERLINE MILES TOTAL
# this_sw/sh_miles is RIGHT LEFT MILES with SW or SH TOTAL
this_sw_sh_miles <- format(round(as.numeric(sum(st_length(this_sw_sh))/5280), 1), 
                           digits = 1, nsmall=1, big.mark=",")
# this_comb_miles is RIGHT LEFT MILES where we could match SW/SH to a road segment
this_comb_miles <- 0
```
```{r, eval=!has_sw_sh & has_roads}
# this_centerline_miles is CENTERLINE MILES TOTAL
this_centerline_miles <- format(round(as.numeric(sum(st_length(this_roads))/5280), 1), 
                           digits = 1, nsmall=1, big.mark=",")
# this_sw/sh_miles is RIGHT LEFT MILES with SW or SH TOTAL
this_sw_sh_miles <- 0
# this_sw/sh_miles is RIGHT LEFT MILES where we could match SW/SH to a road segment
this_comb_miles <- 0
```

>>>>

```{r}

this_geo <- st_as_sf(loop_df) %>% filter(tomatch == "{{current_geo}}") 
if (!is.na(st_crs(this_geo)$epsg)) {
  ncdf <- st_transform(ncdf, st_crs(this_geo)$epsg)
  nc_sw_sh <- st_transform(nc_sw_sh, st_crs(this_geo)$epsg)
}
this_roads <- st_intersection(ncdf, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))

# need to handle the case where this_sw_sh or this_roads has 0 rows
has_roads <- nrow(this_roads) != 0
has_sw_sh <- nrow(this_sw_sh) != 0
has_both <- has_roads & has_sw_sh
# do not evaluate most of this child if does not
this_comb_total_score <-0
```

@@

```{r, eval=has_sw_sh & !has_roads}
this_centerline_miles <- 0 # this_centerline_miles is CENTERLINE MILES TOTAL
# this_sw/sh_miles is RIGHT LEFT MILES with SW or SH TOTAL
this_sw_sh_miles <- format(round(as.numeric(sum(st_length(this_sw_sh))/5280), 1), 
                           digits = 1, nsmall=1, big.mark=",")
# this_comb_miles is RIGHT LEFT MILES where we could match SW/SH to a road segment
this_comb_miles <- 0
```
```{r, eval=!has_sw_sh & has_roads}
# this_centerline_miles is CENTERLINE MILES TOTAL
this_centerline_miles <- format(round(as.numeric(sum(st_length(this_roads))/5280), 1), 
                           digits = 1, nsmall=1, big.mark=",")
# this_sw/sh_miles is RIGHT LEFT MILES with SW or SH TOTAL
this_sw_sh_miles <- 0
# this_sw/sh_miles is RIGHT LEFT MILES where we could match SW/SH to a road segment
this_comb_miles <- 0
